### 2018-06-20 pubs/itp-2018/sections/proof-reconstruction.tex
[ strip ] first finished draft of its description

\input{sections/diagram.tex}
The overview of the proof-reconstruction is presented as a workflow
in Fig.~\ref{fig:proof-reconstruction-workflow} following the same
basis of the proposed workflow presented in~\cite{sultana2015}.

@@

\begin{notation}
  The function name written in \texttt{typewriter} font refers to a
  \Metis inference rule in the \TSTP derivations. The same function
  name written using
  \textsf{sans serif} font refers to our formalized version to
  reconstruct the rule and formally implemented in~\cite{AgdaMetis}.
  To increase the readability for functions and theorems, we use
  the convention \Source and \Target as synonyms of the \Prop
  type. The \Source type in the reconstructed rule definition refers
  to the argument in the \TSTP derivation, \ie the input formula of
  the inference rule. A formula of \Target type refers to the
  expected result of the rule found in the \TSTP derivation.
\end{notation}

\subfile{sections/proof-reconstruction/strip.tex}

Now, as we mention in the beginning of this section, to reconstruct
the \Metis inference rules, we use the following pattern in
the formalization.

\begin{myexamplenum}
\label{ex:inference-rule-pattern}
Let \texttt{metisRule} be a \Metis inference rule. To reconstruct
this rule, we define the function \fun{metisRule} in type theory
that follows the pattern:

@@

To justify all transformations done by the \fun{metisRule} rule, we
prove its soundness with a theorem like the following:

@@

The remainder of this section will be devoted to present a formal
description in type theory of the remaining \Metis rules presented in
Table~\ref{tab:agda-metis-table} using the pattern presented in the
example above. We follow the same order to present the rules as the
table shows.

>>>>

\input{sections/diagram.tex}

The overview of the proof-reconstruction is presented as a workflow
in Fig.~\ref{fig:proof-reconstruction-workflow} following the same
basis of the proposed workflow presented in~\cite{sultana2015}.

@@

\begin{notation}

  The function name written in \texttt{typewriter} font refers to a \Metis
  inference rule in the \TSTP derivations. The same function name written using
  \textsf{sans serif} font refers to our formalized version to reconstruct the
  rule and formally implemented in~\cite{AgdaMetis}. To increase the readability
  for functions and theorems, we use the convention \Source and \Target as
  synonyms of the \Prop type. The \Source type in the reconstructed rule
  definition refers to the argument in the \TSTP derivation, \ie the input
  formula of the inference rule. A formula of \Target type refers to the
  expected result of the rule found in the \TSTP derivation.

\end{notation}

% -----------------------------------------------------------------------------
% -- Strip Rule --
% -----------------------------------------------------------------------------
\subfile{sections/proof-reconstruction/strip.tex}
% -----------------------------------------------------------------------------

The remainder of this section will be devoted to present a formal description in
type theory of the remaining \Metis rules presented in
Table~\ref{tab:agda-metis-table} using the pattern presented in
Example~\ref{ex:inference-rule-pattern}. We follow the same order to present the
rules as the table shows.

\begin{myexamplenum}
\label{ex:inference-rule-pattern}
Let \texttt{metisRule} be a \Metis inference rule in the \TSTP derivations.
To reconstruct this \texttt{metisRule}, we define in the type theory
a function preserving the name of the original rule. This function should follow
the following pattern.

@@

To justify that all transformations performed by the \fun{metisRule} rule are correct, we
will provide a theorem to show its soundness that says:

@@
